{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-04-28 thesis/landslide.tex
work on quotes

\inspirationalquote{Somewhere is the promise of an uncharted trail, with 700 branching limbs and 700 ways to fail.}
{ThouShaltNot, "Cardinal Directions"}

>>>>

\inspirationalquote{Somewhere is the promise of an uncharted trail, with 700 branching limbs and 700 ways to fail.}
{ThouShaltNot, Cardinal Directions}

### 2018-04-28 thesis/thesis.tex
fix incomplete references/labels/citations, move some chapters to their own files
work on quotes

\input{intro}
\input{overview}
\input{landslide}

\chapter{Quicksand}
\inspirationalquote{
% original
% {\footnotesize 嫌な事も悲しい事もあったけど、守りたい物だって沢山この世界にはあったから…} \\
% trans. slightly paraphrased from crunchyroll subtitle; removed "..."s, added past tense for あった
There were awful, sad things in this world.
But there were a lot of things worth protecting, too.
}
{Kaname Madoka, Mahou Shoujo Madoka{\raisebox{0.1em}{$\scriptstyle \bigstar$}}Magica}
%\inspirationalquote{Always, somewhere, someone is fighting for you.
%As long as you remember her, you are not alone.}
%{Mahou Shoujo Madoka{\raisebox{0.1em}{$\scriptstyle \bigstar$}}Magica}

\chapter{Education}
\inspirationalquote{Knowing the students might one day
%find a way to
fix their concurrency bugs...
it fills you with determination.}{Undertale (paraphrased)}

\chapter{Transactions}
%\inspirationalquote{

\chapter{Related Work}
\inspirationalquote{
\begin{tabular}{p{0.58\textwidth}}
To test if your paper makes a genuine contribution to its discipline,
see if you can afford a generous tone in the "Related Work" section.
\end{tabular}}
{Conor McBride}

\chapter{Future Work}
% TODO: ask for permission for this one
% https://twitter.com/Poem4your_sprog/status/878747092788838400
\inspirationalquote{
\begin{tabular}{p{0.54\textwidth}}
A little bit of being kind,
a tiny open door; \\
A nicer slice of peace of mind
begets a little more. \\
It won't correct the world tonight,
nor change tomorrow too; \\
But maybe if you do it right,
you'll find it changes *you*.
\end{tabular}}
{Sam "Poem\_for\_your\_sprog" Garland}

\chapter{Conclusion}
\inspirationalquote{
	\begin{tabular}{p{0.84\textwidth}}
	"If you are a god, Zeus, as the stories claim, then why did you create evolution?
	Why did you make a world that can only grow through cruelty and pain?"
	\\
	For a moment\inspirationalhyphen{}surely this meant death was near\inspirationalhyphen{}she thought she heard him answer:
	"My child, I was shaped by the gods that came before me, as you were shaped by me.
	The choice I had was between creation and oblivion, life and death.
	And I chose life, because any life is better than no life,
	because as long as there is life, there is hope\inspirationalhyphen{}if not for us, then for some generation to come."
	\\
	"Then how are you a god, if you can offer so little?" she whispered, feeling death creep closer.
	\\
	"I am a god because I take upon myself the burden of creation," the statue replied.
	\\
	"Then we are all gods," Alexandra said, and pushed the button.
	\end{tabular}}
%{Galatea, The Talos Principle}
{The Talos Principle}

>>>>

\input{intro}
\input{overview}
\input{landslide}
\input{quicksand}
\input{education}
\input{tm}

\chapter{Related Work}
\label{chap:relatedwork}
\inspirationalquote{
\begin{tabular}{p{0.58\textwidth}}
To test if your paper makes a genuine contribution to its discipline,
see if you can afford a generous tone in the "Related Work" section.
\end{tabular}}
{Conor McBride}

\chapter{Future Work}
\label{chap:warpzone}
% TODO: ask for permission for this one
% https://twitter.com/Poem4your_sprog/status/878747092788838400
\inspirationalquote{
\begin{tabular}{p{0.51\textwidth}}
A little bit of being kind,
a tiny open door; \\
A nicer slice of peace of mind
begets a little more. \\
It won't correct the world tonight,
nor change tomorrow too; \\
But maybe if you do it right,
you'll find it changes you.
\end{tabular}}
{Sam "Poem\_for\_your\_sprog" Garland}

\chapter{Conclusion}
\label{chap:conclusion}
\inspirationalquote{
	\begin{tabular}{p{0.84\textwidth}}
	"If you are a god, Zeus, as the stories claim, then why did you create evolution?
	Why did you make a world that can only grow through cruelty and pain?"
	\\
	For a moment\inspirationalhyphen{}surely this meant death was near\inspirationalhyphen{}she thought she heard him answer:
	"My child, I was shaped by the gods that came before me, as you were shaped by me.
	The choice I had was between creation and oblivion, life and death.
	And I chose life, because any life is better than no life,
	because as long as there is life, there is hope\inspirationalhyphen{}if not for us, then for some generation to come."
	\\
	"Then how are you a god, if you can offer so little?" she whispered, feeling death creep closer.
	\\
	"I am a god because I take upon myself the burden of creation," the statue replied.
	\\
	"Then we are all gods," Alexandra said, and pushed the button.
	\end{tabular}}
%{Galatea, The Talos Principle}
{The Talos Principle}
